---
title: "James Tripp"
output:
  html_document:
    df_print: paged
    theme: united
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(kableExtra)
```

Faculty page: https://warwick.ac.uk/jamestripp

Email: james.tripp@warwick.ac.uk

#### Personal statement

An academic technologist skilled in data analysis, software development, server administration and teaching. I approach my work with enthusiasm, passion and an open mind.

#### Employment

```{r echo=FALSE}
tribble(
  ~ Post, ~ Employer, ~ Dates,
  "Senior Academic Technologist", "University of Warwick", "2018 - 2019",
  "Academic Technologist", "University of Warwick", "2015 - 2018",
  "Postdoctoral Research Fellow", "University of Warwick", "2013 - 2016",
) %>% 
  kable() %>%
  kable_styling(
    full_width = F,
    position = 'left'
    )
```

#### Education

```{r echo=FALSE}
tribble(
  ~ Degree, ~ University, ~ Dates,
  "PhD in Psychology", "University of Warwick", "2010 - 2013",
  "BSc (Hons) in Psychology", "University of Warwick", "2007 - 2010",
) %>% 
  kable() %>%
  kable_styling(
    full_width = F,
    position = 'left'
    )
```
#### Teaching

```{r echo=FALSE}
tribble(
  ~ Module, ~ Dates, ~ Material,
  "IM902: Approaches to the Digital", "2015 - present", '',
  "IM904: Digital Objects, Digital Methods", "2015 - present", '',
  "IM920: Digital Sociology", "2015 - 2017", '',
  "QSTEP Masterclass: Social Media Analysis", "2019", 'Github',
  "QSTEP Quantitative Methods Workshops", "2017", 'Github'
) %>% 
  mutate(
    Material = cell_spec(
      Material, "html",
      link = c('', '', '', 'https://github.com/jamestripp/qstep-socialmedia', 'https://github.com/jamestripp/qstep-workshops')
    )
  ) %>%
  kable('html', escape = FALSE) %>%
  kable_styling(
    full_width = F,
    position = 'left'
    )
```

#### Software Projects

* [LE-CAT](https://github.com/jamestripp/lecat) - Lexicon-based Categorization and Analysis Tool developed by the Centre for Interdisciplinary Methodologies in collaboration with the Media of Cooperation Group at the University of Siegen.

* [Backfillz](https://github.com/WarwickCIM/backfillz) - MCMC visualisations package developed at the University of Warwick and supported by the Turing Institute.

#### References

Available upon request